Multi-Agent Path Finding with Matching using Increasing Cost Tree Search

### 2021-06-07 docs/paper.tex
Added plots for fraction solved
Added description of ID framework

	In practice, joint MDDs are not explicitly constructed but instead a depth-first search is used to search joint MDDs. This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD (which can get rather large) than is necessary for finding a solution.
	\subsubsection{Pruning in ICTS}
	\label{pruning}
	In \cite{sharon2011}, in addition to the basic two-level solver, three pruning methods to speed up search are discussed, two of which were used in this work. All work by taking $j < k$ and applying the described method to each possible combination of $j$ out of $k$ agents. If no solution exists for any such combination, the full $k$-agent low-level search is not triggered. The two basic pruning methods are as follows.
	\begin{enumerate}
		\item Simple pruning: the $j$-agent MDD is searched using DFS for a solution.
		\item Enhanced pruning: the $j$-agent MDD is searched using BFS and when children are generated, for each agent, all children that do not appear in any unified node are removed from the MDD. In \ref{fig:mdds}, the $C$ node of $MDD_1$ would be removed as it cannot be unified with any node of $MDD_2$ at that level. 
	\end{enumerate}
	In addition, repeated enhanced pairwise pruning is described in which the enhanced pruning procedure is repeated for all combinations until a fixpoint is reached, which is when no child node is removed from any of the agent MDDs in an iteration. This was not used in this work.

@@

	\section{Experimental results}
	Because MAPFM lies on the fringe of pathfinding research, no standard benchmarks appear to exist. For MAPF there are the Moving AI benchmarks \cite{sturtevant2012} and potentially a new MAPFM standard benchmark could be defined by generating suitable partitions of agents into teams for these MAPF instances. It was noticed however that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge. This observation informed the creation of a map generator within the peer group

	\begin{figure*}
		\centering
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/open-1}
			\caption{Open, 1 team}
			\label{fig:problem}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/open-3}
		\caption{Open, 3 teams}
		\label{fig:problem}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/obstacle-1}
			\caption{Obstacle, 1 team}
			\label{fig:ict2}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/obstacle-3}
		\caption{Obstacle, 3 teams}
		\label{fig:ict2}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/maze-1}
			\caption{Maze, 1 team}
			\label{fig:mdds}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/maze-3}
			\caption{Maze, 3 teams}
			\label{fig:mdds}
		\end{subfigure}

		\caption{Average solving time of algorithm variants on various types of 20x20 grids with a 30s timeout}
		\label{fig:bottom}
	\end{figure*}
	\section{Responsible Research}
	In experiments used to compare the different MAPFM algorithms within the peer group, care was taken to make the comparison fair: all algorithms are implemented in Python 3 and run on the same system: a server with a 12-core Intel Xeon E5-2683 with 8Gb of RAM dedicated to running experiments for this project. Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.

>>>>

	In practice, joint MDDs are not explicitly constructed but instead a depth-first search is used to search joint MDDs. This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD (which can get rather large) than is necessary for finding a solution.
	\subsubsection{ICTS with Independence Detection}
	Like many other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced in \cite{standley2010}. ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups. If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case ICTS, until no conflicts between groups occur. The goal of ID is to minimize $k'$, the size of the largest group that has to be planned. Optionally, a conflict avoidance table (CAT) can be maintained for use during planning of groups. This records the paths planned by other groups and can facilitate tie-breaking in search that minimizes the number of conflicts; the CAT is omitted from listing \ref{id-algo} for brevity but was implemented and used in experiments.
	\begin{algorithm}
	\begin{algorithmic}[1]
		\State \text{Assign each agent to a singleton group}
		\State \text{plan a path for each group}
		\Repeat
			\State \text{simulate execution of all paths until a conflict occurs}
			\State \text{merge two conflicting groups into a single group}
			\State \text{cooperatively plan new group}
		\Until{\text{no conflicts occur}}
		\State $solution\gets\text{paths of all groups combined}$
		\State \textbf{return solution}
	\end{algorithmic}
	\caption{Simple Independence Detection by Standley} 
	\label{id-algo}
	\end{algorithm}

	\subsubsection{Pruning in ICTS}
	\label{pruning}
	In \cite{sharon2011}, in addition to the basic two-level solver, three pruning methods to speed up search are discussed, two of which were used in this work. All work by taking $j < k$ and applying the described method to each possible combination of $j$ out of $k$ agents. If no solution exists for any such combination, the full $k$-agent low-level search is not triggered. The two basic pruning methods are as follows.
	\begin{enumerate}
		\item Simple pruning: the $j$-agent MDD is searched using DFS for a solution.
		\item Enhanced pruning: the $j$-agent MDD is searched using BFS and when children are generated, for each agent, all children that do not appear in any unified node are removed from the MDD. In \ref{fig:mdds}, the $C$ node of $MDD_1$ would be removed as it cannot be unified with any node of $MDD_2$ at that level. 
	\end{enumerate}
	In addition, repeated enhanced pairwise pruning is described in which the enhanced pruning procedure is repeated for all combinations until a fixpoint is reached, which is when no child node is removed from any of the agent MDDs in an iteration. This was not used in this work.

@@

	\section{Experimental results}
	Because MAPFM lies on the fringe of pathfinding research, no standard benchmarks exist\footnote{That is, to the knowledge of the author.}. For MAPF there are the Moving AI benchmarks \cite{sturtevant2012} and potentially a new MAPFM standard benchmark could be defined by generating suitable partitions of agents into teams for these MAPF instances. It was noticed however that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge. This observation informed the creation of a map generator within the peer group with various parameters. Using this map generator, three types of 20x20 grids were generated:
	\begin{enumerate}
		\item Open: An obstacle-free grid
		\item Obstacle: A grid with some obstacles
		\item Maze: A grid with many obstructed tiles
	\end{enumerate}

	\begin{figure*}
		\centering
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/open-1}
			\caption{Open, 1 team}
			\label{fig:open1}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/open-3}
		\caption{Open, 3 teams}
		\label{fig:open3}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/obstacle-1}
			\caption{Obstacle, 1 team}
			\label{fig:obstacle1}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/obstacle-3}
		\caption{Obstacle, 3 teams}
		\label{fig:obstacle3}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/maze-1}
			\caption{Maze, 1 team}
			\label{fig:m1}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/maze-3}
			\caption{Maze, 3 teams}
			\label{fig:m3}
		\end{subfigure}
		\caption{Average solving time of algorithm variants on various types of 20x20 grids with a 30s timeout}
		\label{fig:bottom}
	\end{figure*}

	\begin{figure*}
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/open-1-p}
		\caption{Open, 1 team}
		\label{fig:open1}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/open-3-p}
		\caption{Open, 3 teams}
		\label{fig:open3}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/obstacle-1-p}
		\caption{Obstacle, 1 team}
		\label{fig:obstacle1}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/obstacle-3-p}
		\caption{Obstacle, 3 teams}
		\label{fig:obstacle3}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/maze-1-p}
		\caption{Maze, 1 team}
		\label{fig:m1}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/maze-3-p}
		\caption{Maze, 3 teams}
		\label{fig:m3}
	\end{subfigure}
	\caption{Fraction solved out of 50 maps of algorithm variants on various types of 20x20 grids with a 30s timeout}
	\label{fig:bottom}
\end{figure*}
	\section{Responsible Research}
	In experiments used to compare the different MAPFM algorithms within the peer group, care was taken to make the comparison fair: all algorithms are implemented in Python 3 and run on the same system: a server with a 12-core Intel Xeon E5-2683 with 8Gb of RAM dedicated to running experiments for this project. Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.
